Effects of Reynolds Number on the Performance and Near-Wake of a Cross-Flow Turbine

### 2014-09-17 paper.tex
Add comment about coordinate system dimensions being in meters
Add todo item for turbine model with no hubs
Add a bunch of stuff

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations.}
\label{fig:wake_locations}
\end{figure}

@@

>>>>

Previously we took a general look at how maximum performance and some 2D wake
profiles are affected by Reynolds number, but here we week to look much deeper.

@@

\todo[inline]{Make sure to use drawing of turbine with no hubs, since these were
included in the tare drag"}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations. Dimensions are in
meters.} 
\label{fig:wake_locations}
\end{figure}

@@

\subsubsection{Mean Momentum Transport}

\todo[inline]{Make bar graph for all $Re$.}

\subsubsection{Dominant Timescales}

\todo[inline]{Look at how spectra change when turbine rotational frequency
changes relative to inertial subrange.}
